---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nolem

<!-- badges: start -->
<!-- badges: end -->

The goal of nolem is to provide an example of how to package up a Shiny application.
The main aims are:

- DIY shiny-as-a-package (without additional packages)
- Use [{bslib}](https://rstudio.github.io/bslib/)
- Styled in NHS branding
- Meets accessibility standards


## Why not use {golem} etc...

There are a number of packages which provide scaffolding for shiny-as-a-package

- [{golem}](https://thinkr-open.github.io/golem/)
- [{rhino}](https://appsilon.github.io/rhino/)
- [{leprechaun}](https://leprechaun.opifex.org/#/)

Personally, I find them a little bit excessive for small projects, and I like having something independent.


## Getting started

This is an example framework showing a DIY shiny-as-a-package. 
I like shiny-as-a-package because you get the benefits of the R CMD check, and because people can run your app easily.

The package isn't really intended to be installed, as it's a demo. 

If you want to run the app, you can with the following

```{r, eval = FALSE}
devtools::install_github("statsRhian/nolem")
nolem::run_app()
```

You can read about it in [Chapter 20 of Mastering Shiny](https://mastering-shiny.org/scaling-packaging.html).
