---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nolem

<!-- badges: start -->
<!-- badges: end -->

The goal of nolem is to provide an example of how to package up a Shiny application.

The main aims are:

- package up a shiny application (without additional packages)
- Use {bslib}
- Meets accessibility standards


## Why not use {golem} etc...

There are a number of packages which provide scaffolding for shiny-as-a-package

- {golem}
- {rhino}
- {leprechaun}

Personally, I find them a little bit excessive for projects, and I like having something independent.


## Getting started

This is an example framework, to help people learn about shiny as a package. 
I like shiny-as-a-package because you get the benefits of the R CMD check, and because people can run your app easily

```{r, eval = FALSE}
install.packages("nolem")
nolem::run_app()
```

You can read about it in [Chapter 20 of Mastering Shiny](https://mastering-shiny.org/scaling-packaging.html).
